### 2018-12-29 papers/journal/experiments.tex
Added comparision table for SAT and SMT tool's timing.
Experiments section update

\textbf{{\sattool} (Bounded model checker based tool)}:
	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%	
\todo{SA: CBMC Diagram}	
In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\subsection{Results}
The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.

@@

In Table~\ref{tab:smt-grph}, we present the running times for the search of
VTSs for {\smttool} of sizes 2 to 10 that satisfy the variants and compare with the {\sattool}.
%
For the comparison between both encodings we have fixed the total
number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and $|M| = 2|N| + 1$ for $|N| = 2$.
%
For each variant, we fix maximum number of parallel
edges to 2.
%
In the table we have shown comparison for specific connectivity, for
example variant A is checked against any graph with connectivity 2,
variant B with connectivity 3 similarly for the rest of the Variants.
%

%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 s
ecs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Using this encoding in comparison to the old one, not only we got effi
ciency improved for finding a SAT model but also did better in the cas
e of refutation that no model exist (Table 2 Variant A timing comparis
on and Variant D with N =2). 
%
Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ n
odes.

\input{qbf-table}
%\textbf{Universal Condition:}
Table~\ref{tab:qbf-graph} presents the result of the QBF tool.

@@

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}
In the table, we are reporting five synthesis queries
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%  and was able to
% fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
% The tool was able to synthesize the Boolean functions in 470s.
%
To illustrate the versatility of our tool, the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%  and was able to
% synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of edges, and labels
of node and labels.

>>>>

\textbf{{\sattool} (Bounded model checker based tool)}:
	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
\todo{SA: CBMC Diagram}	
The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%

In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\subsection{Results}
The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph} and table~\ref{tab:satsmt-graph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.

@@

In table~\ref{tab:smt-grph} we present the minimal connectivity results for each variation of the existential condition. 
%
Table~\ref{tab:satsmt-graph} present the comparision of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we fixed the total number of molecules ($|M|$) to be $2|N|$ 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation F, of 2-connected 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
%
In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologicly relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.

\input{qbf-table}
%\textbf{Universal Condition:}
\todo{SA: Will add after experimentations.}
Table~\ref{tab:qbf-graph} presents the result of the QBF tool.

@@

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.  
%
The fig shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}

In the Fig~\ref{tab:synth-graph}, we report five synthesis queries.
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%  and was able to
% fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
% The tool was able to synthesize the Boolean functions in 470s.
%
To illustrate the versatility of our tool, the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%  and was able to
% synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of edges, and labels
of node and labels.
